MT Post Farm Analysis Report

### 2024-03-06 eag.qmd
commit 3/6/24

fid_plot <- 
filled_data %>%
  dplyr::select(MeasRetTime, Area, Height) %>%
  mutate(Height = ifelse(MeasRetTime < 3.2, 0, Height))
  # ggplot() +
  # geom_point(aes(x = MeasRetTime, y = Height)) +
  # geom_line(aes(x = MeasRetTime, y = Height)) +
  # theme_bw()
eag_plot <-
eag %>%
  mutate(row_num = row_number()) %>%
  rename("EAD" = 'EAD 1') 
ggplotly(
ggplot() +
  geom_line(data = fid_plot, aes(x = MeasRetTime, 
                                 y = Height), 
            color = "red") +
  geom_line(data = eag_plot, aes(x = scale_values(row_num), 
                                 y = EAD * 100), 
            color = "blue") +

  scale_y_continuous(name = "EAD", sec.axis = sec_axis(~./100, name = "Height")) + 
  labs(title = "Comparison of EAD and Height",
       x = "Row Number (Scaled)", 
       y = "EAD",
       color = "Legend") +
  theme_bw() + 
  scale_x_continuous(breaks = seq(min(fid_plot$MeasRetTime,
                                      max(fid_plot$MeasRetTime), 
                                      by = 1)))
)

>>>>

fid_plot <- 
filled_data %>%
  dplyr::select(MeasRetTime, Area, Height) %>%
  mutate(Height = ifelse(MeasRetTime < 3.2, 0, Height))
  # ggplot() +
  # geom_point(aes(x = MeasRetTime, y = Height)) +
  # geom_line(aes(x = MeasRetTime, y = Height)) +
  # theme_bw()
eag_plot <-
eag %>%
  mutate(row_num = row_number()) %>%
  rename("EAD" = 'EAD 1') 
ggplotly(
ggplot() +
  geom_line(data = fid_plot, aes(x = MeasRetTime, 
                                 y = Height), 
            color = "red") +
  geom_line(data = eag_plot, aes(x = scale_values(row_num)+1.2, 
                                 y = EAD * 100), 
            color = "blue") +

  scale_y_continuous(name = "EAD", sec.axis = sec_axis(~./100, name = "Height")) + 
  labs(title = "Comparison of EAD and Height",
       x = "Row Number (Scaled)", 
       y = "EAD",
       color = "Legend") +
  theme_bw() 
)

### 2024-03-06 field_report.qmd
commit 3/6/24

---
title: "MT Field Site Analysis Report"
author: "Jackson Strand"
date: "`r Sys.Date()`"
output: 
  quarto::quarto_html:
    layout: sidebar
    theme: cosmo
    toc: true
    toc_float: true
    toc_title: "Table of Contents"
    toc_collapsed: false
    toc_depth: 4
    # number_sections: true
editor_options: 
  chunk_output_type: console
---
```{r library, echo = F, message = F, warning = F}
library(tidyverse)
library(readxl)
library(ggplot2)
library(kableExtra)
library(plotly)
```
```{r column.order, echo = F}
column.order <- c("distance", "collection", "p.inf", 
                  "p.cut", "p.par", "poten")

@@

# POST FARM

### Plant Selection and Cages

Assessment of C. cinctus infestation and mortality within B. inermis were assessed using a 34 x 60 ft plot at the Arthur H. Post Agronomy Farm (43°38'19.39"N, 116°14'28.86"W), an extension research station of Montana State University in Bozeman, MT. The cage structure was built using 1-inch PVC piping with the netting made using 530\(\mu\) Amber Lumite Screen (BioQuip® Products, LLC). Twelve cages were built to dimensions of 6ft x 3ft x 3ft (L x W x H) with cage locations selected randomly based on the space available within the plot and arranged in sets of three. The cages were removed from the plot after 3 weeks of sawfly release.

### Insects

Wheat stem stubble was collected in Three Forks, MT, USA (43°38'19.39"N, 116°14'28.86"W) from fields that experienced high levels of C. cinctus infestation and cutting in the prior year. Cut stubble, which contained C. cinctus larvae in diapause, were kept refrigerated between -2°C and 3°C for >100 days as required to complete obligatory larval diapause. As needed, stubs were removed from refrigeration and kept at 22-27°C for 4-5 weeks inside of 100 oz GladWare® storage containers (Glad®, Oakland, California USA). Stubs were added to cages once B. inermis stems reached six inches tall, with sawfly quantity treatments as follows: high (600 stubs), low (200 stubs), and control (0 stubs).

#### Data Collection

Stems were collected from each cage site in late August. All stems from each 6 x 3 ft cage section were collected. Each stem was sliced open using X-Acto® knives to collect data on infestation, dead larvae, live larvae, and parasitism at each internode.

### Overall WSS Infestation and Cutting

```{r (pf.RAW) post farm n.inf data, echo = F, message = F}
pf.raw.2022 <- read_excel("/Users/jacksonstrand/Library/CloudStorage/OneDrive-MontanaStateUniversity/Data/BWW/Field/Post\ Farm/2022/Post\ Farm\ 2022.xlsx", sheet = "n.inf")
pf.raw.2023 <- read_excel("/Users/jacksonstrand/Library/CloudStorage/OneDrive-MontanaStateUniversity/Data/BWW/Field/Post\ Farm/2023/Post\ Farm\ 2023.xlsx", sheet = "n.inf")
```
```{r (pf.inf.23) post farm inf data, echo = F}
pf.inf.23 <- read_excel("/Users/jacksonstrand/Library/CloudStorage/OneDrive-MontanaStateUniversity/Data/BWW/Field/Post\ Farm/2023/Post\ Farm\ 2023.xlsx", sheet = "inf") %>%
  rename(n.1 = 8, n.2 = 9, n.3 = 10, n.4 = 11,
         n.5 = 12, n.6 = 13, n.7 = 14, n.8 = 15,
         n.9 = 16, n.10 = 17)
```
```{r (pf.comb) post farm data combined, echo = F}
# 2022
pf.2022.site <-
pf.raw.2022 %>%
  group_by(treatment, site) %>%
  reframe(site, treatment,
            p.inf = sum(iv, ir, ix)/sum(uv, ur, iv, ir, ix),
            cut = sum(cut)/sum(total),
            total.stems = sum(iv, ir, ix, uv, ur)) %>%
  unique() %>%
  pivot_longer(-c(treatment, total.stems, site),
               names_to = "type",
               values_to = "percent") %>%
  mutate(year = "2022")

# 2023
pf.2023.site <-
pf.raw.2023 %>%
  group_by(treatment, site) %>%
  reframe(treatment, site, 
          t.inf = sum(n.iv, n.ir, n.ix),
          p.inf = sum(n.iv, n.ir, n.ix)/sum(n.uv, n.ur, 
                                            n.iv, n.ir, n.ix),
          cut = sum(cut)/sum(total),
          total.stems = sum(n.iv, n.ir, n.ix, n.uv, n.ur)) %>%
  distinct() %>%
  pivot_longer(-c(treatment, total.stems, site),
               names_to = "type",
               values_to = "percent") %>%
  filter(!type == "t.inf") %>%
  arrange(type) %>%
  mutate(year = "2023")

pf.comb <-
  pf.2022.site %>%
  rbind(pf.2023.site) %>%
  group_by(treatment, year, type) %>%
  mutate(count = n(),
         average = mean(percent),
         sd = sd(percent),
         se = (sd/sqrt(count))) %>%
  reframe(treatment, year, type,
          mean = mean(percent),
          sd = mean(sd),
          se = mean(se)) %>%
  unique()

```
```{r (pf.total) pf total stems, echo = F}
# 2022 totals
pf.2022.total <-
  pf.raw.2022 %>%
  group_by(treatment) %>%
  reframe(total = sum(uv, ur, iv, ir, ix)) %>%
  mutate(year = "2022")

# 2023 totals
pf.2023.total <-
  pf.raw.2023 %>%
  group_by(treatment) %>%
  reframe(total = sum(n.uv, n.ur, n.iv, n.ir, n.ix)) %>%
  mutate(year = "2023")

pf.total.comb <-
  pf.2022.total %>%
  rbind(pf.2023.total)

#### Basic Table and Plot of Infestation

```{r post farm table, echo = F, results = 'asis'}
pf.23.table <-
pf.comb %>%
  filter(year == "2023") %>%
  dplyr::select(treatment, type, mean) %>%
  mutate(mean = round_based_on_size(mean)) %>%
  pivot_wider(values_from = mean,
              names_from = type,
              values_fn = list(mean = mean)) %>%
  left_join(pf.2023.total, by = "treatment")

pf.22.table <-
pf.comb %>%
  filter(year == "2022") %>%
  dplyr::select(treatment, type, mean) %>%
  mutate(mean = round_based_on_size(mean)) %>%
  pivot_wider(values_from = mean,
              names_from = type,
              values_fn = list(mean = mean))  %>%
  left_join(pf.2022.total, by = "treatment")

pf.23.table.final <-
kable(pf.23.table[c("treatment", "total", "p.inf", "cut")], 
      caption = "2023 Post Farm Infestation", 
      format = "html",
      col.names = c("Treatment", "Total Stems", "% Inf", "% Cut"),
      align = "lccc") %>%
  kable_styling(full_width = FALSE,
                bootstrap_options = c("striped", "bordered", "hover")) %>%
  row_spec(0, background = "#f2f2f2")

pf.22.table.final <-
kable(pf.22.table[c("treatment", "total", "p.inf", "cut")], 
      caption = "2022 Post Farm Infestation", 
      format = "html",
      col.names = c("Treatment", "Total Stems", "% Inf", "% Cut"),
      align = "lcc") %>%
  kable_styling(full_width = FALSE,
                bootstrap_options = c("striped", "bordered", "hover")) %>%
  row_spec(0, background = "#f2f2f2")

cat('<div style="display: flex;">')
cat('<div style="flex: 1;">')
cat(pf.23.table.final)
cat('</div>')
cat('<div style="flex: 1;">')
cat(pf.22.table.final)
cat('</div>')
cat('</div>')
```

```{r post farm plot, echo = F, fig.height = 2.5, fig.align = 'center'}
pf.comb <-
pf.comb %>%
  left_join(pf.total.comb, by = c("treatment", "year"))

ggplot() +
  facet_wrap(~treatment) +
  geom_bar(stat = "identity",
           position = position_dodge(),
           data = pf.comb %>%
             filter(type == "p.inf"),
           aes(year, mean, fill = "p.inf")) +
  geom_bar(stat = "identity",
           position = position_dodge(),
           data = pf.comb %>%
             filter(type == "cut"),
           aes(year, mean, fill = "cut")) +
  geom_errorbar(data = pf.comb,
                aes(x = year,
                    ymin = mean - se,
                    ymax = mean + se),
                position = position_dodge(0.9),
                width = 0.2,
                alpha = 0.5) +
  theme_bw() +
  labs(x = element_blank(),
       y = "Percentage of stems (%)",
       fill = element_blank()) +
  scale_fill_brewer(palette = "Greens",
                    labels = c("Cut", "Infested"))

Let's take a closer look at the number of nodes borrowed through by the larvae. Using this information we can make an arguement about the size and length of time each larvae was alive prior to dying. This can be informative in understanding how many larvae would have been left later in the season for potential parasitism.

#### Infestation Percentage/Node

```{r v.r infestation node, echo = F, warning = F, message = F, fig.height = 3.5, fig.align = 'center'}
v.r_inf <- 
pf.inf.23 %>%
  dplyr::select(site, rep, treatment, 8:19) %>%
  mutate(stem.id = row_number()) %>%
  pivot_longer(-c(stem.id, site, rep, treatment, v.r, lar),
               names_to = "node",
               values_to = "node_status") %>%
  na.omit() %>%
  group_by(stem.id, treatment, v.r, lar) %>%
  reframe(nodes.inf = n()) %>%
  group_by(treatment, v.r, lar, nodes.inf) %>%
  reframe(count = n()) %>%
  group_by(treatment, v.r) %>%
  mutate(count2 = sum(count),
         per = count/count2) %>%
  reframe(treatment, v.r, nodes.inf, per) %>%
  mutate_at(vars(nodes.inf), as.factor)

# plot
v.r_inf %>%
  ggplot() +
  geom_bar(stat = "identity",
         position = position_dodge(),
         aes(y = per, x = nodes.inf, fill = treatment)) +
  geom_line(stat = "smooth",
            aes(y = per, 
                x = nodes.inf, 
                group = treatment, 
                color = treatment),
            se = FALSE,
            alpha = 0.6,
            linewidth = 1.3,
            linetype = "solid",
            method = "loess") +
  theme_bw() +
  scale_fill_brewer(palette = "Greens") +
  scale_color_brewer(palette = "Reds") +
  facet_wrap(~v.r)

# anova
anova1 <- 
  summary(aov(per ~ treatment + nodes.inf + v.r, data = v.r_inf))

aov.df <- as.data.frame(anova1[[1]])
aov.df$`Pr(>F)` <- sprintf("%.4f", aov.df$`Pr(>F)`)
aov.df$Source <- rownames(aov.df)
rownames(aov.df) <- NULL

aov.df[,2:4] <- round(aov.df[,2:4], 3)

# anova table
kbl(aov.df %>%
      dplyr::select(Source, everything()), 
    align = "lccccc",
    format = "html",
    caption = "ANOVA Table",
    col.names = c("", "Df", "Sum Sq", "Mean Sq", "F-Value", "Pr(>F)")) %>%
  kable_styling(bootstrap_options = c("striped", "bordered", 
                                      "hover", "repsonsive"),
                full_width = FALSE) %>%
  row_spec(0, background = "#f2f2f2")

Based on the results of our ANOVA, we have weak evidence (Pval = `r aov.df[3,5]`) to suggest there is a difference in the number of nodes infested when considering treatment group and vegetative and reproductive stems.

```{r cumsum of infestation per node, echo = F, fig.align = "center"}
# I want to see the percentage of stems with 6+ nodes infested, then 5:6+, then 4:6+, etc.
cumsum <-
pf.inf.23 %>%
  dplyr::select(site, rep, treatment, 8:19) %>%
  mutate(stem.id = row_number()) %>%
  pivot_longer(-c(stem.id, site, rep, treatment, v.r, lar),
               names_to = "node",
               values_to = "node_status") %>%
  na.omit() %>%
  group_by(stem.id, treatment, v.r, lar) %>%
  reframe(nodes.inf = n()) %>%
  group_by(treatment, nodes.inf) %>%
  reframe(count = n()) %>%
  group_by(treatment) %>%
  mutate(count2 = sum(count),
         per = count/count2) %>%
  reframe(treatment, nodes.inf, per) %>%
  arrange(treatment, desc(nodes.inf)) %>%
  group_by(treatment) %>%
  mutate(cumsum = cumsum(per)) %>%
  mutate_at(vars(nodes.inf), as.factor) %>%
  dplyr::select(treatment, nodes.inf, cumsum) %>%
  mutate(nodes.inf = fct_rev(nodes.inf))

cumsum %>%
  mutate(cumsum = round(cumsum, 2)) %>%
  rename("Treatment" = treatment) %>%
  pivot_wider(values_from = "cumsum",
              names_from = "nodes.inf") %>%
  kable("html",
        caption = "Cumulative sum of nodes infested",
        align = "lcccccc") %>%
  kable_styling(full_width = FALSE,
                bootstrap_options = c("bordered", "hover")) %>%
  row_spec(0, background = "#f2f2f2") %>%
  add_header_above(c(" ", "# of Nodes Infested" = 6))

ggplot(data = cumsum,
         aes(x = nodes.inf,
             y = cumsum,
             group = treatment, 
             color = treatment)) +
  geom_line() +
  theme_bw() +
  geom_bar(stat = "identity",
           aes(x = nodes.inf, 
               y = cumsum,
               fill = treatment),
           position = position_dodge(),
           alpha = 0.25) +
  theme_bw() +
  labs(x = "Number of Nodes Infested",
       y = "Cumulative sum % of stems",
       fill = "WSS Treatment \nLevel",
       color = "WSS Treatment \nLevel",
       title = "Smooth brome node infestation") +
  scale_x_discrete(limits = rev(levels(cumsum$cumsum)))

I like this plot because it shows the cumulative percentage sum of nodes infested at each node. For example, at the 3rd node in 2023, we see that close to 70% of the stems in the 'high' treatment group exhibited between 3 and 6 nodes infested. As a general thought exercise, the more nodes a larvae burrowed through, the larger the larvae. This means that if we classify a "large" larvae as one who burrowed through at least 4 nodes, our infestation data shows that 36% of the larvae in the 'high' treatment groups died as "large" larvae.

```{r larvae breakdown, echo = F}
# how many stems had live larvae in them?
# percent of stems with each larval type

larvae.type <-
pf.inf.23 %>%
  dplyr::select(site, rep, treatment, 8:19) %>%
  mutate(stem.id = row_number()) %>%
  pivot_longer(-c(stem.id, site, rep, treatment, v.r, lar),
               names_to = "node",
               values_to = "node_status") %>%
  na.omit() %>%
  group_by(treatment, lar) %>%
  reframe(count = n()) %>%
  mutate(year = "2023") %>%
  left_join(pf.total.comb, by = c("treatment", "year")) %>%
  group_by(treatment) %>%
  mutate(per = count/total) %>%
  filter(lar == "a") %>%
  mutate(per = round(per, 3))
# stems collected in late October. This is much later than if parasitoids were flying.

kable(larvae.type[c("treatment", "count", "total", "per")],
      format = "html",
      align = "c",
      col.names = c("Treatment", "Count", "Total Stems", "%"),
      caption = "Stems with Living Larvae (2023)") %>%
  kable_styling(bootstrap_options = c("striped", "bordered", 
                                      "hover", "repsonsive"),
                full_width = FALSE) %>%
  row_spec(0, background = "#f2f2f2")
```

Interesting to see that `r larvae.type[1,6]*100`% of stems in the 'high' treatment groups and `r larvae.type[2,6]*100`% of stems in the 'low' treatment group had living WSS larvae. The stems for this experiement were harvested in late October, much later in the season when we would expect the second generation parasitoids to be searching for a host.

<hr>

@@

```
```{r (n.inf) brome join, echo = F}
n.inf <-
raw.2023 %>%
  dplyr::select(site, year, location, collection, 
              n.uv, n.ur, n.iv, n.ir, n.ix, 
              cut, e, c)  %>%
  bind_rows(raw.2022 %>%
              rename(n.uv = uv,
                     n.ur = ur,
                     n.iv = iv,
                     n.ir = ir,
                     n.ix = ix) %>%
              dplyr::select(site, year, location, collection, 
                    n.uv, n.ur, n.iv, n.ir, n.ix, 
                    cut, e, c)) %>%
  group_by(site, location, collection, year) %>%
  mutate(inf = sum(n.iv, n.ir, n.ix),
         total = sum(n.uv, n.ur, n.iv, n.ir, n.ix)) %>%
  ungroup() %>%
  dplyr::select(-c(n.uv, n.ur, n.iv, n.ir, n.ix)) %>%
  mutate(p.inf = inf/total,
         p.par = (c + e)/inf,
         p.cut = cut/inf,
         poten = (cut + c + e)/inf) %>%
  pivot_longer(-c(site, location, collection, year),
               names_to = "type",
               values_to = "value") %>%
  group_by(location, collection, year, type) %>%
  distinct() %>%
  mutate(distance = "brome",
         location = case_when(
           location == "kw" ~ "k",
           location == "ke" ~ "k", 
           TRUE ~ location))
```
```{r (stubble.brome) join stubble/brome, echo = F}
# join the stubble data and the brome data
stubble.brome <-
joined.stubble %>%
  pivot_longer(-c(site, location, distance, year, collection),
               names_to = "type",
               values_to = "value") %>%
  distinct() %>%
  rbind(n.inf) %>%  # rbind the brome data
  filter(!type == "total") %>%  # remove type = "total"
  mutate(type = case_when(
    type == "c" ~ "p",
    type == "e" ~ "p",
    TRUE ~ type)) %>% # replace the e and c variables with p, for simplicity
  ungroup() %>%
  dplyr::select(-site) %>%
  group_by(location, distance, year, collection, type) %>%
  reframe(mean = mean(value),
         count = n(),
         sd = sd(value),
         se = sd/sqrt(count)) %>%
  distinct() %>%
  filter(type %in% c("p.inf", "p.cut", "p.par", "poten")) %>%
  distinct()
```

```{r, echo = F, eval = F}
stubble.brome %>%
  filter(location == "g",
         distance %in% c("20", "5"),
         year == "2023",
         collection == "fall")
```

>>>>

---
title: "MT Field Site Analysis Report"
author: "Jackson Strand"
date: "`r Sys.Date()`"
output: 
  html:
    # layout: sidebar
    theme: cosmo
    toc: true
    toc_float: true
    toc_title: "Table of Contents"
    toc_expand: true
    toc_depth: 4
    # number_sections: true
editor_options: 
  chunk_output_type: console
toc: true
toc_title: "Table of Contents"
# toc_expand: true
# toc_float: true
---
<!-- field site cover image -->
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Image Cropping Example</title>
<style>
    }
    .image-container {
        width: auto; /* Set the width of the container */
        height: auto; /* Set the height of the container */
        overflow: hidden; /* Hide overflow */
    }
    .image-container img {
        width: 100%; /* Make the image fill the container horizontally */
        height: auto; /* Maintain aspect ratio */
        object-fit: cover;
        object-position: center;
    }
</style>
</head>
<body>

<div class="image-container">
    <img src="img/field-sites/big-sandy-wide.jpg" alt="Your Image">
</div>

</body>
</html>

```{r library, echo = F, message = F, warning = F}
library(tidyverse)
library(readxl)
library(ggplot2)
library(kableExtra)
library(plotly)
```
```{r column.order, echo = F}
column.order <- c("distance", "collection", "p.inf", 
                  "p.cut", "p.par", "poten")

@@

@@

```
```{r (n.inf) brome join, echo = F}
n.inf <-
raw.2023 %>%
  dplyr::select(site, year, location, collection, 
              n.uv, n.ur, n.iv, n.ir, n.ix, 
              cut, e, c)  %>%
  bind_rows(raw.2022 %>%
              rename(n.uv = uv,
                     n.ur = ur,
                     n.iv = iv,
                     n.ir = ir,
                     n.ix = ix) %>%
              dplyr::select(site, year, location, collection, 
                    n.uv, n.ur, n.iv, n.ir, n.ix, 
                    cut, e, c)) %>%
  group_by(site, location, collection, year) %>%
  mutate(inf = sum(n.iv, n.ir, n.ix),
         total = sum(n.uv, n.ur, n.iv, n.ir, n.ix)) %>%
  ungroup() %>%
  dplyr::select(-c(n.uv, n.ur, n.iv, n.ir, n.ix)) %>%
  mutate(p.inf = inf/total,
         p.par = (c + e)/inf,
         p.cut = cut/inf,
         poten = (cut + c + e)/inf) %>%
  pivot_longer(-c(site, location, collection, year),
               names_to = "type",
               values_to = "value") %>%
  group_by(location, collection, year, type) %>%
  distinct() %>%
  mutate(distance = "brome",
         location = case_when(
           location == "kw" ~ "k",
           location == "ke" ~ "k", 
           TRUE ~ location))
```
```{r (stubble.brome) join stubble/brome, echo = F}
# join the stubble data and the brome data
stubble.brome <-
joined.stubble %>%
  pivot_longer(-c(site, location, distance, year, collection),
               names_to = "type",
               values_to = "value") %>%
  distinct() %>%
  rbind(n.inf) %>%  # rbind the brome data
  filter(!type == "total") %>%  # remove type = "total"
  mutate(type = case_when(
    type == "c" ~ "p",
    type == "e" ~ "p",
    TRUE ~ type)) %>% # replace the e and c variables with p, for simplicity
  ungroup() %>%
  dplyr::select(-site) %>%
  group_by(location, distance, year, collection, type) %>%
  reframe(mean = mean(value),
         count = n(),
         sd = sd(value),
         se = sd/sqrt(count)) %>%
  distinct() %>%
  filter(type %in% c("p.inf", "p.cut", "p.par", "poten")) %>%
  distinct()
```
```{r, echo = F, eval = F}
stubble.brome %>%
  filter(location == "g",
         distance %in% c("20", "5"),
         year == "2023",
         collection == "fall")
```

### 2024-03-06 locoweed-report.qmd
commit 3/6/24

---
title: "All Locoweed Analysis Report"
author: "Jackson Strand"
date: '`r format(Sys.Date())`'
output: 
  html_document:
    toc: true
    code_folding: hide
bibliography: citations/citations.bib
link-citations: true
cls: council-of-science-editors-author-date.csl
editor_options: 
  chunk_output_type: console
---

@@

# Random Forest
library(ranger)
library(MVN) # for normality test
```

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Image Cropping Example</title>
<style>
    }
    .image-container {
        width: auto; /* Set the width of the container */
        height: auto; /* Set the height of the container */
        overflow: hidden; /* Hide overflow */
    }
    .image-container img {
        width: 100%; /* Make the image fill the container horizontally */
        height: auto; /* Maintain aspect ratio */
        object-fit: cover;
        object-position: center;
    }
</style>
</head>
<body>

@@

@@

## Field Volatile Collection
### Boxplot Comparison
```{r all comparison boxplot, echo = F, fig.align = 'center'}
joined.data.clr %>%
  # pivot to make all compounds in one column
  pivot_longer(-c(plant.id, year, swa, type, pair2),
               names_to = "compound",
               values_to = "ngghr") %>%
  # ggplot code
  ggplot(aes(compound, ngghr, fill = swa)) +
  geom_boxplot(position = position_dodge(width = 0.9),
                 outlier.color = NA,
                 alpha = 0.5) +
  geom_jitter(aes(compound, ngghr),
              alpha = 0.3,
              position = position_jitterdodge(jitter.width = 0.2,
                                              dodge.width = .8),
              show.legend = FALSE,
              # pch = 21, 
              stroke = 0, 
              size = 1.5) +
  theme(axis.text.x = element_text(angle = 45, 
                                    hjust = 1),
        legend.background = element_rect(color = "black"),
        # legend.position = c(0.8,0.9),
        panel.background = element_rect(fill = "white"),
        axis.line = element_line(color = "black"),
        panel.grid.major.x = element_line(color = "#F2F2F2")) +
  labs(x = element_blank(),
       y = "VOC quantity (CLR(ng/g/hr))",
       title = "2022/23 Field Locoweed Volatile Profile Comparison") +
  scale_fill_discrete(name = "Endophyte",
                      labels = c("Not Present", "Present"))
```

>>>>

---
title: "Locoweed Volatiles"
author: "Jackson Strand"
date: '`r format(Sys.Date())`'
output: 
  html_document:
    toc: true
    code_folding: hide
bibliography: citations/citations.bib
link-citations: true
cls: council-of-science-editors-author-date.csl
editor_options: 
  chunk_output_type: console
toc: true
---

@@

# Random Forest
library(ranger)
library(MVN) # for normality test
library(plotly)
```

<!-- bee cover image -->
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Image Cropping Example</title>
<style>
    }
    .image-container {
        width: auto; /* Set the width of the container */
        height: auto; /* Set the height of the container */
        overflow: hidden; /* Hide overflow */
    }
    .image-container img {
        width: 100%; /* Make the image fill the container horizontally */
        height: auto; /* Maintain aspect ratio */
        object-fit: cover;
        object-position: center;
    }
</style>
</head>
<body>

@@

*Note: This project is still a work in progress.*

@@

## Field Volatile Collection
### Boxplot Comparison
```{r all comparison boxplot, echo = F, fig.align = 'center'}

joined.data.clr %>%
  # pivot to make all compounds in one column
  pivot_longer(-c(plant.id, year, swa, type, pair2),
               names_to = "compound",
               values_to = "ngghr") %>%
  # ggplot code
  ggplot(aes(compound, ngghr, fill = swa)) +
  geom_boxplot(position = position_dodge(width = 0.9),
                 outlier.color = NA,
                 alpha = 0.5) +
  geom_jitter(aes(compound, ngghr),
              alpha = 0.3,
              position = position_jitterdodge(jitter.width = 0.2,
                                              dodge.width = .8),
              show.legend = FALSE,
              # pch = 21, 
              stroke = 0, 
              size = 1.5) +
  theme(axis.text.x = element_text(angle = 45, 
                                    hjust = 1),
        legend.background = element_rect(color = "black"),
        # legend.position = c(0.8,0.9),
        panel.background = element_rect(fill = "white"),
        axis.line = element_line(color = "black"),
        panel.grid.major.x = element_line(color = "#F2F2F2")) +
  labs(x = element_blank(),
       y = "VOC quantity (CLR(ng/g/hr))",
       title = "2022/23 Field Locoweed Volatile Profile Comparison") +
  scale_fill_discrete(name = "Endophyte",
                      labels = c("Not Present", "Present"))

### 2024-03-06 msu-masters.qmd
commit 3/6/24

  .text p {
    font-size: 14px;
    margin-top: 5px;
    color: #666;
  }
</style>
</head>
<body>
  <a href="wss.qmd" class="container">
    <div class="content">
      <img src="img/msu-masters/wss.JPG" alt="Image"> <!-- Center the image within the box -->
      <div class="text">
        <h1>Wheat Stem Sawfly</h1>
        <p>Understanding the importance of smooth brome in promoting a Braconid parasitoid that targets the Wheat Stem Sawfly.</p>
      </div>
    </div>
  </a>
  <a href="https://www.example.com" class="container">
    <div class="content">
      <img src="img/msu-masters/loco-bee2.jpg" alt="Image"> <!-- Center the image within the box -->
      <div class="text">
        <h1>Locoweed Volatiles</h1>
        <p>Comparison of volatile organic compounds profiles of <em>Oxytropis</em> plants that contained the commensal endophyte <em>Alternaria oxytropis</em> and those that did not.</p>
      </div>
    </div>
  </a>
</body>
</html>

>>>>

  .text p {
    font-size: 14px;
    margin-top: 5px;
    color: #666;
  }
</style>
</head>
<body>
  <a href="wss.qmd" class="container">
    <div class="content">
      <img src="img/msu-masters/wss.JPG" alt="Image"> <!-- Center the image within the box -->
      <div class="text">
        <h1>Wheat Stem Sawfly</h1>
        <p>Understanding the importance of smooth brome in promoting a Braconid parasitoid that targets the Wheat Stem Sawfly.</p>
      </div>
    </div>
  </a>
  <a href="locoweed-report.qmd" class="container">
    <div class="content">
      <img src="img/msu-masters/loco-bee2.jpg" alt="Image"> <!-- Center the image within the box -->
      <div class="text">
        <h1>Locoweed Volatiles</h1>
        <p>Comparison of volatile organic compounds profiles of <em>Oxytropis</em> plants that contained the commensal endophyte <em>Alternaria oxytropis</em> and those that did not.</p>
      </div>
    </div>
  </a>
</body>
</html>

### 2024-03-06 pfreport.qmd
commit 3/6/24

---
title: "MT Post Farm Analysis Report"
author: "Jackson Strand"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    toc_title: "Table of Contents"
    toc_collapsed: false
    toc_depth: 4
    # number_sections: true
editor_options: 
  chunk_output_type: console
---
```{r library, echo = F, message = F, warning = F}
library(tidyverse)
library(readxl)
library(ggplot2)
library(kableExtra)
library(plotly)
```
```{r column.order, echo = F}
column.order <- c("distance", "collection", "p.inf", 
                  "p.cut", "p.par", "poten")

>>>>

---
title: "MT Post Farm Analysis Report"
author: "Jackson Strand"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    toc_title: "Table of Contents"
    toc_collapsed: false
    toc_depth: 4
    # number_sections: true
editor_options: 
  chunk_output_type: console
toc: true
---
```{r library, echo = F, message = F, warning = F}
library(tidyverse)
library(readxl)
library(ggplot2)
library(kableExtra)
library(plotly)
```
```{r column.order, echo = F}
column.order <- c("distance", "collection", "p.inf", 
                  "p.cut", "p.par", "poten")
